---
title: "SOP"
author: "Kathan"
date: "1 October 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Study Oriented Project Analysis

This displays all the results and analysis done on the data-set created for the SOP.

```{r,echo=FALSE}
#Reading in data,modifying it,initiating libraries.
data<-read.csv("Final_Data.csv")
data<-data[1:42,]
suppressWarnings(suppressMessages(library(tseries)))
suppressWarnings(suppressMessages(library(ggplot2)))
suppressWarnings(suppressMessages(library(vars)))
suppressWarnings(suppressMessages(library(urca)))
for(i in c(3,4,5,6,10)){
  data[,i]<-log10(data[,i])
}
oil<-data[,10]
agri<-data[,3]
manu<-data[,4]
const<-data[,5]
trans<-data[,6]
DF<-data.frame(oil,agri,manu,const,trans)
```
##Checking Stationarity for all parameters
###Agriculture
```{r,echo=FALSE}
###Agriculture
suppressWarnings(kpss.test(diff(data[,3])))
```
###Manufacturing
```{r,echo=FALSE}
###Manufacturing
suppressWarnings(kpss.test(diff(data[,4])))
```
###Construction
```{r,echo=FALSE}
###Construction
suppressWarnings(kpss.test(diff(data[,5])))
```
###Transport
```{r,echo=FALSE}
###Transport
suppressWarnings(kpss.test(diff(data[,6])))
```
###Oil
```{r,echo=FALSE}
###Oil
suppressWarnings(kpss.test(diff(data[,10])))
```
##Co-Integration Tests
###All 5 parameters taken as a group
```{r}
CoInt1<-ca.jo(DF,type="trace",K=2)
summary(CoInt)
CoInt2<-ca.jo(DF,type="eigen",K=3,spec="longrun")
summary(CoInt)
```
###Determing proper lag length of the input matrix for VAR Model
```{r}
VARselect(data.frame(data[,3],data[,4],data[,5],data[,6],data[,10]))$selection
```
###Creating VAR Model
```{r}
var_est<-VAR(DF,p=3,type="const")
VECM<-cajorls(CoInt,r=2)
VAR<-vec2var(CoInt,r=2)
summary(VECM)
```
###Impulse Response Functions
```{r}
irf_est<-irf(var_est,impulse="oil",response=c("agri","manu","const","trans"),n.ahead=3,ortho =TRUE)
plot(irf_est)
```
###Forecast Error Variance Decomposition
```{r}
fevd(var_est,n.ahead=3)
```
###Granger Causality Tests
```{r}
causality(var_est,cause="oil")
```
